An open source scientific article about extrasolar magma oceans

### 2022-08-06 src/tex/ms.tex
restructure, include magmaocean model schematic

%\begin{deluxetable*}{cc}
%\tablecaption{Confirmed and suggested trends in the exoplanet population}
%%\tablewidth{\pagewidth}
%\tablehead{\colhead{Trend} & \colhead{Reference}}
%\startdata
%missing sub-Saturn mass valley in M-dwarf planetary systems &  Schlecker et al., subm. \\
%$\cdots$ & $\cdots$
%\enddata
%\tablecomments{We show a list of population-level trends that have been reported in demographic studies or predicted from planet formation theories.}
%\end{deluxetable*}
%
%\begin{deluxetable*}{cccccc}
%\tablecaption{Confirmed and suggested trends in the exoplanet population}
%%\tablewidth{\pagewidth}
%\tablehead{\colhead{No.} & \colhead{Trend} & \colhead{Reference} & \colhead{Terrestrials}&\colhead{Roman}&\colhead{Plato}}
%\startdata
%%\hline
%%Theoretically predicted&&&&&
%%\\
%%\hline
%%1&High occurrence of low-mass planets at a few au&\citep{Penny2019}&FALSE&TRUE&FALSE \\
%%2&(super-)Earth occurrence drops again for very low-mass stars&Mulders2021, (Schlecker2021a)&TRUE&TRUE&TRUE
%%\\
%%3&Hot Jupiter - cold Jupiter relation&Schlaufman \& Winn (2016)&FALSE&TRUE&FALSE
%%\\
%%4&super-Earth composition-architecture link&Schlecker+2021a&TRUE&FALSE&FALSE
%%\\
%
%\enddata
%\tablecomments{We show a list of population-level trends that have been reported in demographic studies or predicted from planet formation theories.}
%\end{deluxetable*}

Several patterns in the planetary parameter space have been reported in demographic studies or predicted from planet formation theories.

\section{Synthetic star and planet sample}

\section{The magma ocean hypothesis}

\subsection{Global magma oceans}
\todo[inline]{introduce magma oceans and their influence on planetary radii~\citep{Dorn2021}.\\ Might also be already fully covered in the Introduction section}

@@

@@

@@

\subsection{Synthetic planet populations with and without magma oceans}
\todo{describe the way we inject magma oceans into the synthetic planet population with Bioverse}
\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/has_magmaocean.pdf}
        \caption{Synthetic planets with and without magmaoceans as a function of Solar-equivalent semi-major axis}
        \label{fig:has_magmaocean}
    \end{centering}
\end{figure*}

\section{Survey simulation}

\subsection{Testing the magma ocean hypothesis with current and planned exoplanet missions}
\todo{PLATO, Ariel, LIFE?, Nautilus\\ What are threshold missions that are able to detect this signal? =>X meter working for Y years, or X' meter working for Y' years => conclusion could be that there is interesting science to do with intermediate size telescope.
 }

@@

>>>>

\section{Global magma oceans and their imprint on exoplanet demographics}
\todo[inline]{"Methods Section" for the geophysical models.}
\subsection{Global magma oceans}
\todo[inline]{introduce geophysical model.\\ Introduce its parametrization either here or further down when modeling demographic imprint.\\ Figure~\ref{fig:magmaocean_model} goes here.}

%\begin{figure}
\begin{figure}[!ht]
    \begin{centering}
        \includegraphics[width=\hsize]{figures/magmaocean_model.jpg}
        \caption{Schematics of the geophysical model framework.}
        \label{fig:magmaocean_model}
    \end{centering}
\end{figure}

@@

\Blindtext[1]

@@

\subsubsection{Synthetic planet populations with and without magma oceans}
\todo{describe the way we inject magma oceans into the synthetic planet population with Bioverse}
\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/has_magmaocean.pdf}
        \caption{Synthetic planets with and without magmaoceans as a function of Solar-equivalent semi-major axis}
        \label{fig:has_magmaocean}
    \end{centering}
\end{figure*}

\subsection{Testing the magma ocean hypothesis with current and planned exoplanet missions}
\todo{Introduce survey simulation(s). PLATO, Ariel, LIFE?, Nautilus\\ What are threshold missions that are able to detect this signal? =>X meter working for Y years, or X' meter working for Y' years => conclusion could be that there is interesting science to do with intermediate size telescope.}

@@

@@

\begin{note}
    \textit{Here or in the introduction:} For observations of rocky exoplents, the currently best-probed regime is hot, close-in planets.
    These bodies experience climatic conditions that are similar to the environment of the inner Solar System bodies at early stages of their formation.
    Studies of the geophysical state and evolution of hot exoplanets can thus contribute to our understanding of the early formation stages of Earth and other habitable worlds.
\end{note}
